\documentclass[resmargin]{res}
	\linespread{1.15}
	\newsectionwidth{1.26in}
	\sectionskip=4.25ex
	\addtolength{\textwidth}{0.5in}
	\addtolength{\textheight}{2in}
	\addtolength{\oddsidemargin}{-0.25in}

\usepackage{enumitem}\setlist{nosep}
%\usepackage[utf8]{inputenc}
\usepackage{helvet}\renewcommand{\familydefault}{\sfdefault}
\usepackage{multicol}\setlength\multicolsep{0.0in}

\begin{document}

\name{\textbf{\LARGE{Stuart Miller}}\\[6pt]}

\address{505 Peace St.\\Pella, IA 50219}
\address{816-785-4105\\stewythe1st@gmail.com}

\begin{resume}

\hspace{-1.26in}\noindent\rule{7.0in}{0.4pt}

\section{Objective}
To obtain an internship or co-op for 2018 in the field of embedded software engineering.

\section{Experience}
Vermeer Corporation \hfill Pella, IA\\
{\bf Embedded Software Engineer II} \hfill May 2021 - Present\\
{\bf Embedded Software Engineer I} \hfill May 2019 - May 2021\\
{\bf Embedded Software Engineer Co-Op} \hfill May 2018 - Dec. 2018
\begin{itemize}
	\item Develop machine control software for Vermeer's next generation horizontal directional drills using Simulink and C/C++.
	\item Develop display software using Qt, representing the first Vermeer drill with touchscreen capabilities.
	\item Architect the software, hardware, and system integration of a common platform for all next-generation horizontal directional drills.
	\item Design future-proof systems based on the needs of current automation features as well as desires for expansion and R\&D.
	\item Bring the first horizontal directional drill on the common platform, the Vermeer D550 to market.
	\item Troubleshoot software, electrical, hydraulic, and mechanical problems in collaboration with other engineering teams.
	\item Drive development towards purpose-build in-house software solutions instead of relying on proprietary programming environments and tools from specific vendors.
	\item Collaborate with hardware vendors to introduce new controller hardware, purpose-built for Vermeer's needs, and oversee its adoption into the existing programming environment.
	\item Introduce CI/CD workflows using Github Actions; whereas previously all builds \& tests were run manually.
	\item Work extensively on new low level common hardware abstraction layer C code to be shared across segments of the company.
	\item Develop a communication scheme based on SAE J1939 DM14-DM16 messages for automatic adjustment, retention, and secure transferral of protected parameters between machine control units.
	\item Complete an accelerated project to update port legacy software to new hardware when supply chain constraints threatened key product lines.

\end{itemize}
Garmin International \hfill Olathe, KS\\
{\bf Software Engineering Intern, Aviation} \hfill Oct. ‘15 - Aug. ‘16
\begin{itemize}
	\item Developed and tested software used on aviation displays and user interfaces
	\item Worked closely within the constraints of hardware to write effective embedded C code
	\item Completed a refactor of part of Garmin's module testing environment to allow for enhanced software verification at the system level
	\item Participated in software development lifecycle activities such as code reviews, software verification, and code coverage analysis

\end{itemize}

\newpage

The Boeing Company \hfill St. Louis, MO\\
{\bf IT Intern, Business Systems Data Warehouse \& Analytics} \hfill May ’15 - Aug. ‘15
\begin{itemize}
	\item Worked closely with offshore resources to manage the transition of finance web portal code from Adobe Coldfusion to ASP .NET
	\item Provided analysis on existing PL/SQL Queries and database structure
	\item Used Tableau analysis software to create data visualizations and dashboards
\end{itemize}

\iffalse
Missouri S\&T IT Department \hfill Rolla, MO\\
{\bf IT Help Desk Senior Student Technician} \hfill Oct. ’14 - Present
\begin{itemize}
	\item Investigate computer related problems, determine the cause, and implement a solution or coordinate with the appropriate department to resolve the issue
	\item Serve as a point of escalation for demanding issues
	\item Oversee training of new employees and implementation of new policies
	\item Operate and manage the 3D printers available to faculty and students
	\item Repair laptops as a Dell-certified technician
\end{itemize}
\fi

\section{Education}
Missouri University of Science and Technology (Missouri S\&T)\hfill May 2019 \\
{\bf M.S. Computer Engineering}\\%\hfill	{\bf GPA: 3.8/4.0} \\
{\bf \it Emphasis in embedded systems}

Missouri University of Science and Technology (Missouri S\&T)\hfill May 2017 \\
{\bf B.S. Computer Engineering}\\%\hfill	{\bf GPA: 3.8/4.0} \\
{\bf \it Minors in Computer Science \& Mathematics}\\

\section{Skills}
\begin{multicols}{3}
	C / C++\\
	Linux / Embedded Linux\\
	SAE J1939 \& CAN bus\\
	Test-Driven Development\\
	\\
	Qt\\
	Git Version Control\\
	CI / CD\\
	Hardware Troubleshooting\\
	\\
	GNU Make / Makefiles\\
	Matlab / Simulink\\
	Jira Project Management\\
	Software Requirements\\
\end{multicols}


\iffalse
\section{Projects}
Senior Design Project, Missouri S\&T\hfill Spring 2017\\
{\bf Digital Music Transcriber}
\begin{itemize}
	\item Designed an algorithm to convert audio input from musical instruments to written music using a Texas Instruments C2000-series processor
	\item Implemented code to interface with open-source display and audio-processing libraries
	\item Worked as part of a development team, participating in weekly standups and collaboration meetings
	\item Acted as team leader to help manage schedules and coordinate documentation
\end{itemize}

Missouri S\&T Artificial Intelligence Tournament\hfill Fall 2016\\
{\bf Third Place Winner}
\begin{itemize}
	\item Designed a C++ program capable of playing competitive chess
	\item Utilized AI state-space search techniques such as minimax, alpha-beta pruning, and quiescence.
	\item Defeated both human and other artificial intelligence opponents to win third place
\end{itemize}
\fi

\iffalse
\section{Honors \& Activities}
Missouri S\&T Chancellor's Scholarship\\
Missouri Higher Education Scholarship (Bright Flight)\\
James C. Grimm Electrical \& Computer Engineering Scholarship\\
Tau Beta Pi - National Engineering Honor Society\\
Kappa Kappa Psi - National Honorary Band Fraternity\\
Principal Oboist - Missouri S\&T Symphonic Orchestra and Wind Symphony
\fi

\end{resume}

\end{document}